---
title             : "The Impact of Measurement Practices and Measurement Error on Construct Validity and Replication Outcomes in Psychological Science"
shorttitle        : "Measurement Quality and Replicability"

author: 
  - name          : "Goos, C."
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Professor Cobbenhagenlaan 125, 5037 DB, Tilburg, The Netherlands"
    email         : "casgoos99@gmail.com"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Investigation"
      - "Methodology"
      - "Visualization"
      - "Writing - Original Draft Preparation"
      - "Writing - Review & Editing"
  - name          : "Nuijten, M.B."
    affiliation   : "1"
    role:
      - "Project Administration"
      - "Writing - Review & Editing"
      - "Supervision"

affiliation:
  - id            : "1"
    institution   : "Tilburg University"

authornote: |
  1 Department of Methodology and Statistics, Tilburg School of Social and Behavioral Sciences, Tilburg University, Tilburg, NL. 

  Enter author note here. Caspar?

abstract: |
  Recently, the influence of measurement related issues on replicability has received more investigations. 
  In particular, studies have indicated that low reliability, and poor measurement reporting can negatively influence the replicability of an effect. 
  Building on this new line of research, this thesis assessed these influences in large scale replication projects. 
  Protocols from the Many Labs replication projects, and the original articles that the replications were based on were used to assess the  reporting of the measures, while publicly available data from the Many Labs replications was used to assess the reliability of the measures. Reliability did not relate to replicability, and was generally consistent between labs for each measure in the Many Labs projects. 
  The quality of measurement reporting in replication protocols did however relate to replicability.
  Additionally, tentative evidence was found for a relation between quality of measurement reporting in the protocol of a replication and the quality of measurement reporting in its related original study.
  Recommendations are given for researchers and replicators in order to improve measurement practices in replication, and ward its negative impact on replicability. 
  Additionally, directions are given for future research investigating the relationship between measurement issues and replicability.


keywords          : "reliability, measurement, measurement reporting, replicability, construct validity"
wordcount         : "X"

bibliography      : ["r-references.bib", "references.bib"]

floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
knit              : worcs::cite_all
---

```{r setup, include = FALSE}
# loading R libraries
library("papaja")
library("worcs")

# loading source script
source(file = "../source_script.R")

# Code below loads the processed data. The raw data was prepared for analysis in 'prepare_data.R.
# load_data(worcs_directory = "../../Data/AnalysisData") 

# creates a reference list for all used R packages and the installed R version (does not include Rstudio)
r_refs("r-references.bib")
```

This manuscript uses the Workflow for Open Reproducible Code in Science [WORCS version 0.1.1, @vanlissaWORCS2021] to ensure reproducibility and transparency. All code <!--and data--> are available at <https://github.com/CasGoos/WORCSPersonalTemplate.git>.

This is an example of a non-essential citation [\@ @vanlissaWORCS2021]. If you change the rendering function to `worcs::cite_essential`, it will be removed.

```{r analysis-preferences}
# Seed for random number generation
set.seed(31102023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction

## Measurement Error

## Questionable Measurement Practices

# Method

## Sample

### Replication Datasets

### Preregistered Replication Protocols

### Original Study

## Data Collection

## Measures

### Measurement Error Measures

### Replicability Measure

### QMP measures

### Validity Measure

## Analyses

### Analyses Measurement Error

### Analyses QMPs

### Exploratory Analyses

# Results

## Descriptives

## Reliability

## Questionable Measurement Practices

## Exploratory Results

# Discussion

## Quality of Measurement

## Impact on replicability

## Limitations & Future Research

## Implications for Research and Replications in Psychological Science

# Conclusion

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::
